library(data.table)
Cyclic phase analysis - fMRI4
Full Design Structure: G/NG First continuous phase, Tax/Adhoc Cyclic, Final G Continuous Phase

Reading in the data file:
```{r}
install.packages("lme4")  
library(data.table)
fMRI4_cyclic_data <- fread('/Users/channingeveridge/Downloads/Cycle.csv', stringsAsFactors = TRUE)
str(fMRI4_cyclic_data)

```  
lmer syntax:  + signs after one indicate slope, after | what youre setting intercept for
Fixed effects are significant if null and model are signficantly different

Tried many combinations of slopes/intercepts to see which maximum structure would converge. Very difficult. Below is an example that did NOT converge
```{r}
library(lme4)
start <- Sys.time()
intxmodel0 <- lmer(Cyclic.RT ~ RelType + Relatedness + SuperCycle + RelType*Relatedness + Relatedness*SuperCycle  + RelType*Relatedness*SuperCycle + 
              (1+RelType|prompt) +
              (1+Relatedness|prompt) +
              (1+SuperCycle|prompt) +
              (1+RelType*Relatedness|prompt) +
              (1+RelType|ID) +
              (1+Relatedness|ID) +
              (1+SuperCycle|ID) +
              (1+RelType*Relatedness|ID),
           data = fMRI4_cyclic_data, control = lmerControl(optimizer = 'Nelder_Mead', optCtrl = list(maxfun = 100000)))
summary(intxmodel0)
```
Best fit so far:

```{r}
library(lmerTest)
intxmodelcyc <- lmer(Cyclic.RT ~ Generation + RelType + Generation*RelType*Relatedness + Generation*SuperCycle + Relatedness + SuperCycle + RelType*Relatedness + RelType*Relatedness*SuperCycle +
            (1+Relatedness|ID) +
            (1+Relatedness|prompt),
           data = fMRI4_cyclic_data, control = lmerControl(optimizer = 'Nelder_Mead', optCtrl = list(maxfun = 100000)))
summary(intxmodelcyc)


lsme```
This model converges fairly quickly

Results:

Generation itself NOT sig, GenxRelType SIG, RelType SIG, Relatedness SIG, SuperCycle NOT SIG, RelTypexRelatedness SIG, RelType*SuperCycle NOT SIG

Relatedness, RelType*Relatedness, RelType*SuperCycle Sig in RM analysis

```
Null model for testing:
```{r}
nullmodelcyc <- lmer(Cyclic.RT ~ +
             (1+SuperCycle|ID) +
           (1+SuperCycle|prompt),
           data = fMRI4_cyclic_data, control = lmerControl(optimizer = 'Nelder_Mead', optCtrl = list(maxfun = 100000)))
nullmodelcyc

anova(nullmodelcyc,intxmodelcyc)



library(emmeans)
emmeans(intxmodelcyc,pairwise~RelType|Generation)
emmeans(intxmodelcyc,pairwise~Relatedness|RelType)
emmeans(intxmodelcyc, pairwise~RelType*Relatedness|SuperCycle, at = list(SuperCycle = 1:3))

