Reading in the file:
```{r}
library(data.table) 
fMRI4_contfinal_data <- fread('/Users/channingeveridge/ContFinal.csv', stringsAsFactors = TRUE)
str(fMRI4_contfinal_data)
```  
A model that converges:
```{r}
library(lme4)
intxmodelfcont1 <- lmer(LastContinuous.RT ~ Generation + RelType + Relatedness + Quartile + RelType*Relatedness +
           (1+Relatedness*Quartile|Subject) +
           (1+Quartile|Item),
           data = fMRI4_contfinal_data, control = lmerControl(optimizer = 'Nelder_Mead', optCtrl = list(maxfun = 100000)))
intxmodelfcont1
```
Trying a model with added intx of fixed factors:

```{r}
library(lmerTest)
intxmodelfcont2 <- lmer(LastContinuous.RT ~ Generation + RelType + Relatedness + Quartile + RelType*Quartile + Relatedness*RelType+ RelType*Relatedness*Quartile + Relatedness*Quartile +
           (1+RelType*Quartile|Subject) +
           (1+Quartile|Item),
           data = fMRI4_contfinal_data, control = lmerControl(optimizer = 'Nelder_Mead', optCtrl = list(maxfun = 100000)))
summary(intxmodelfcont2)

```
Results: 

Quartile and RelType*Quartile only sig, corroborated with results of previous RM analysis

Testing against null model:
```{r}

nullcont2 <- lmer(LastContinuous.RT ~
           (1+RelType*Quartile|Subject) +
           (1+Quartile|Item),
           data = fMRI4_contfinal_data, control = lmerControl(optimizer = 'Nelder_Mead', optCtrl = list(maxfun = 100000)))
nullcont2

anova(nullcont2,intxmodelfcont2)


library(emmeans)
emmeans(intxmodelfcont2, pairwise~Quartile, at = list(Quartile = 1:4))
emmeans(intxmodelfcont2, pairwise~RelType|Quartile, at = list(Quartile = 1:4))

